%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Web3 \& Open Source}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Next.js, Tamagui, Convex, Solidity, ERC-1155, USDC} % Technologies
    {Mint Up! - Full-Stack Web3 Event Management Platform} % Project name
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {\textbf{Award Winner:} Finalist in Base Builder Quest \#9 (0.25 ETH Prize) — Recognized for UX excellence and technical implementation.}
        \item {Co-developed a Farcaster mini app that gives onchain communities native tooling for event creation, ticketing, and ongoing engagement.}
        \item {Deployed gas-optimized ERC-1155 contracts in Solidity allowing batch-minting of tickets with split-payment routing (Free/USDC)}
        \item {Engineered a ground-up authentication pipeline that blends Farcaster Sign-In With Farcaster (SIWF) and NextAuth for secure, seamless sessions.}
        \item {Shipped a responsive, mobile-first UI with Next.js and Tamagui tailored for The Base App experience and standalone web access.}
        \item {\faLink \href{https://devfolio.co/projects/mint-up-5d5d}{ Submission} \quad | \quad \faLink \href{https://farcaster.xyz/miniapps/jkuOonikCzn7/mint-up}{ Mini App}}
      \end{cvitems}
    }

%---------------------------------------------------------
  \vspace{6mm}

  \cventry
    {Next.js, TypeScript, Convex, Tailwind CSS, Web3} % Technologies
    {SkillBased - Decentralized Professional Identity} % Project name
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Developed a decentralized certification platform where professional credentials are minted as tamper-proof NFTs.}
        \item {Implemented on-chain social validation logic allowing peer-to-peer endorsement of skills.}
        \item {\faGithub\ \href{https://github.com/mavix21/SkillBased}{ GitHub Repo} \quad | \quad \faLink\ \href{https://skill-based.vercel.app/}{ Live Site}}
      \end{cvitems}
    }

%---------------------------------------------------------
  \vspace{6mm}
  \cventry
    {Next.js, Convex, Solidity, TypeScript, Tailwind CSS} % Technologies
    {Buildea - Web3 Education and Reputation Platform} % Project name
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Built an all-in-one platform for developer communities that centralizes workshop management, overcoming traditional tooling limitations by integrating multimedia resources, quizzes, and metrics into a single flow.}
        \item {Architected a real-time gamification and evaluation engine with Convex, supporting complex quiz logic, Arcade level systems, and automated deliverable validation through the GitHub API.}
        \item {Implemented a custom CMS with rich-text editing and file uploads, enabling organizers to curate dynamic educational content and assign hands-on tasks.}
        \item {Designed the \textquotedblleft Proof of Build\textquotedblright{} infrastructure, linking off-chain progress (attendance and grades) to on-chain ERC-1155 credentials to create a verifiable, immutable skills record.}
        \item {\faLink\ \href{https://app.buildea.dev/}{ Live Site}}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
