%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Personal Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {SkillBased - Decentralized Professional Identity} % Project name
    {Next.js, TypeScript, Convex, Tailwind CSS, Web3} % Technologies
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {A full-stack social platform enabling users to mint their professional certifications as NFTs, creating a verifiable and tamper-proof record of skills. Other users can endorse these certificates, adding a layer of social validation on-chain.}
        \item {\faGithub\ \href{https://github.com/mavix21/SkillBased}{GitHub Repo} \quad | \quad \faLink\ \href{https://skill-based.vercel.app/}{Live Demo}}
      \end{cvitems}
    }

%---------------------------------------------------------
  \vspace{6mm}
  \cventry
    {Mint Up! - Full-Stack Web3 Event Management Platform} % Project name
    {Next.js, Tamagui, Convex, Solidity, ERC-1155, USDC} % Technologies
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Selected as a finalist in Base Builder Quest \#9 on Devfolio, earning a 0.25 ETH prize. \quad \faLink\ \href{https://devfolio.co/projects/mint-up-5d5d}{Submission} \quad | \quad \faLink\ \href{https://farcaster.xyz/miniapps/jkuOonikCzn7/mint-up}{Mini App}}
        \item {Co-developed a Farcaster mini app that gives onchain communities native tooling for event creation, ticketing, and ongoing engagement.}
        \item {Implemented a gas-efficient ERC-1155 smart contract in Solidity to batch-mint NFT tickets with both free and USDC-paid options routed directly to organizers.}
        \item {Engineered a ground-up authentication pipeline that blends Farcaster Sign-In With Farcaster (SIWF) and NextAuth for secure, seamless sessions.}
        \item {Shipped a responsive, mobile-first UI with Next.js and Tamagui tailored for The Base App experience and standalone web access.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \vspace{6mm}
  \cventry
    {Personal Portfolio Website} % Project name
    {Astro, TypeScript, Tailwind CSS} % Technologies
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {My personal website, built with Astro for optimal performance and static generation. The project demonstrates a commitment to clean design, minimalism, and choosing the right tool for the job. The code is open-source.}
        \item {\faGithub\ \href{https://github.com/mavix21/portfolio}{GitHub Repo} \quad | \quad \faLink\ \href{https://marcelo-vizcarra.netlify.app/}{Live Site}}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
