%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects \& Open Source}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Next.js, React, TypeScript, Tailwind CSS, Convex} % Technologies
    {Mint Up! - Full-Stack Event Management Platform} % Project name
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {\textbf{Recognition:} Selected as a finalist in the global \textquotedblleft Base Builder Quest \#9\textquotedblright{} competition, highlighted for the quality of its UX and the technical strength of its implementation.}
        \item {Built a Next.js App Router application with SEO-aware routing, metadata, and clean URL structure; integrated REST and typed APIs for event creation, registration, and credential distribution flows.}
        \item {Designed a reusable component system with Tailwind CSS and Tamagui, implementing responsive, pixel-perfect UIs from Figma.}
        \item {\faLink \href{https://devfolio.co/projects/mint-up-5d5d}{ Submission} \quad | \quad \faLink \href{https://farcaster.xyz/miniapps/jkuOonikCzn7/mint-up}{ Mini App}}
      \end{cvitems}
    }

%---------------------------------------------------------
  \vspace{6mm}

  \cventry
    {Next.js, React, TypeScript, Tailwind CSS, Convex} % Technologies
    {SkillBased - Professional Identity Platform} % Project name
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Platform for issuing verifiable professional credentials, featuring peer-validation mechanisms that generate a distributed reputation model.}
        \item {Structured the codebase around component-based design and separation of concerns, with proper metadata and routing for search visibility.}
        \item {\faGithub\ \href{https://github.com/mavix21/SkillBased}{ GitHub Repo} \quad | \quad \faLink\ \href{https://skill-based.vercel.app/}{ Live Site}}
      \end{cvitems}
    }

%---------------------------------------------------------
  \vspace{6mm}
  \cventry
    {Next.js, React, TypeScript, Tailwind CSS, Convex} % Technologies
    {Buildea - Education and Reputation Platform} % Project name
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {All-in-one platform for developer communities that centralizes workshops, multimedia resources, quizzes, and metrics in a single flow.}
        \item {Built a custom, API-driven CMS with rich-text editing and file uploads to curate dynamic content and assign tasks, following a headless-CMS style workflow.}
        \item {Architected a real-time gamification and evaluation engine for complex quiz logic, levels, and GitHub API-based deliverable validation.}
        \item {\faLink\ \href{https://app.buildea.dev/}{ Live Site}}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
